Pomace: a Grappa for Non-Volatile Memory

### 2012-12-11 doc/nvm2013/paper.tex
changes (largely) to section 1

While Grappa’s current design scales to the limit of available network
bandwidth, it does so only for applications whose working set resides
in RAM.  Unfortunately, provisioning systems with petabytes of RAM is
costly, energy inefficient, and likely to increase the time to prepare
for and recover from faults.

@@

\subsection{Challenges in using commodity SSDs}
Grappa’s goal is to provide good irregular application performance on
commodity hardware. Unfortunately, commodity non-volatile memories are
difficult to use in this way for three reasons:

@@

\subsubsection{Using future memory technologies}

@@

\section{Conclusion}
Efficient execution of irregular applications on large datasets is of
growing importance.  Grappa promises to address this need on mass
market clusters.  Addition of non-volatile storage is a natural
extension of such systems.  We ask, what would developing a Pomace for
Grappa -- a Grappa system exploiting non-volatile memory -- entail and
what capability and efficiency improvements might it bring to Grappa’s
application space.  Answering this question is an opportunity for
collaboration between our group and the NVMW community.

>>>>

While Grappa's current design scales to the limit of available network
bandwidth, it does so only for applications whose working set resides
in RAM.  Unfortunately, provisioning systems with petabytes of RAM is
costly, energy inefficient, and likely to increase the time to prepare
for and recover from faults.

@@

\subsection{Challenges in using commodity SSDs}
Grappa's goal is to provide good irregular application performance on
commodity hardware. Unfortunately, commodity non-volatile memories are
difficult to use in this way for three reasons:

@@

v\subsubsection{Using future memory technologies}

@@

\section{Conclusion}
Efficient execution of irregular applications on large datasets is of
growing importance.  Grappa promises to address this need on mass
market clusters.  Addition of non-volatile storage is a natural
extension of such systems.  We ask, what would developing a Pomace for
Grappa -- a Grappa system exploiting non-volatile memory -- entail and
what capability and efficiency improvements might it bring to Grappa's
application space.  Answering this question is an opportunity for
collaboration between our group and the NVMW community.
